Home

### 2017-12-09 analysis/index.Rmd
Files commited by wflow_commit.

>>>>

Click here to check the [RMSE for the rank one example in the paper](MSErank1sim.html)

#### GTEx Z-score

Here is a example to run `flashr2` on RCC [RCC template](GTEXzscoreTemplate.html)

#### missing data imputation

click here to check the template for [missing data imputation with OCV](templateforOCV.html)

click here to check the comparison of different options for FLASH [different shrink options](compareOptionsOCV.html)
